%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{lorena}{matus}
       {International Business Enthusiast}

% In the aside, each new line forces a line break
\begin{aside}
  \section{Contact information}
    Brännkyrkagatan 119
    117 28 Stockholm
    Sweden
    ~
    \href{mailto:lorena-matus@hotmail.com}{lorena-matus@hotmail.com}
    +46 72 537 34 35
  \section{Languages}
    Bilingual Spanish/English
    Novice in Swedish
  \section{Usual comments}
    Honest \& Loyal
    Responsible
    Good learnability
    Handle pressure
    Nice \& social 
    Team player
\end{aside}

\section{Objectives}
    My short term goal is to learn and perfect my Swedish by working in a Swedish environment, where I be able to continue to bring my Swedish to the next level.
    My long term professional goal is to run my own import/export company, since I have a strong interest for international trades and business.

\section{Education}

\begin{entrylist}
  \entry
    {2006 - 2010}
    {Bachelor Degree in International Business}
    {With honors (B.Ib. cum laude)}
    {Universidad Autónoma de Baja California, Tijuana México.
    {\emph{Student and Member of University Council.}}}
\end{entrylist}

\section{Experience}

\begin{entrylist}
  \bigentry
    {2014 - 2015}
    {ProMexico, Stockholm \newline 
        {\href{http://www.promexico.gob.mx/en/mx/stockholm}{promexico.gob.mx}}
    }
    {Internship and project manager}
    {\emph{ProMexico is the official agency
    for attraction of FDI and promotion of exports within the Mexican government. The office is
    part of the Mexican embassy in Sweden and is in charge of the business in the Nordic and Baltic region. 
    During my internship I helped the exports 
    department, my assignment was mainly to assist, advice and 
    support foreign companies already established in Mexico and/or
    foreign investors to invest in Mexican ventures.
    }
    }
    {\textit{ Based on my performance I was hired to fill for a colleague, who took
    leave of absence in June - August 2015.}}
  \bigentry
    {03–07 2014}
    {Restaurant Los Remedios, Tijuana, Mexico \newline
        {\href{http://www.losremedios.mx/}{losremedios.mx}}
    }
    {Hostess}
    {\emph{During this time I was in charge of the customer service,
    reservations, special events and accommodations.}}
    {\textit{ During the expansion of the franchise, and based on my 
    performance, they offer me the administration position of the 
    new establishment.}}

  \entry
    {2011 - 2013}
    {High Chaparral, Hillerstorp \newline
        {\href{http://www.highchaparral.se/sv/}{highchaparral.se}}
    }
    {Summer job, Professional dancer}
    {\emph{I was working as a dancer and co-team leader for the Mexican show at High Chaparral
    theme park. My assignment included, coordinating the dance group, dance practices and show
    performance, acting, appearing as a part of the law enforcement of the outlaw town
    "Old Mexico", Occasionally helping waiting staff.}}
  \entry
    {03–05 2012}
    {World Trade Center, Tijuana, Mexico \newline
        {\href{http://www.wtctijuana.com/}{wtctijuana.com}}
    }
    {Organizing and administration}
    {\emph{During this time I was in charge of the logistic, 
    events, organizing and schedule meetings.
    I was part of the committee for the trading between
    Mexico and USA.}}
  \entry
    {01–05 2011}
    {VIDRIERA TORRE AGUACALIENTE S.A de C.V, Tijuana, Mexico}
    {Administrative assistant}
    {\emph{This company are dedicated to sell glass for windows, cars, 
    offices, etc. During my time I was in charge of customer 
    service, the budget, scheduling meetings and deliveries.}}
\end{entrylist}

\begin{entrylist}
  \entry
    {2008 - 2010}
    {MARMOL Y GRANITO S.A de C.V, Tijuana, Mexico}
    {Summer job, Administrative assistant}
    {\emph{Mármol y granito is one of the biggest retailers of
    marble in Tijuana, during my time I was in charge of 
    customer service, taking customer calls, scheduling 
    deliveries etc. I also did budget work and business 
    meeting scheduling.}}
\end{entrylist}

\section{Academic experience}
\begin{entrylist}
  \entry
    {2006 - 2010}
    {University General Committee Member}
    {Universidad Autónoma de Baja California, Tijuana}
    {This committee was in charge of the budget of the 
    university as well form the new curricula.}
  \entry
    {2009 - 2010}
    {University Career Committee Member}
    {Universidad Autónoma de Baja California, Tijuana}
    {During my last year I was in charge of the business seminars
    organized by the University.}
\end{entrylist}

\section{Other activities}

\begin{entrylist}
  \entry
    {2014 - present}
    {Dancer and dance teacher in Sweden}
    {Member of the Mexico Lindo, dance group}
    {The group is situated in Hornstull where I teach the Mexican traditional dance group. We are preforming at
    reoccurring events every year usually by request from the Mexican embassy.}
  \entry
    {2000 - 2014}
    {Dancer and dance teacher}
    {́Member of the Folk Dance Group Yii Má}
    {The group is from de Lázaro Cárdenas High School, Tijuana, 
    México. I was training dancing and dance teaching. Member of the
    dancing crew preforming at the park High Chaparral in Sweden.}
  \entry
    {07-08 2007}
    {Dancer}
    {́Member of the Folk Dance Group Yii Má}
    {Performed in the dance festival "Cork Folk
    Dance Festival" in Ireland and Amsterdam.}
  \entry
    {07-08 2006}
    {Dancer}
    {́Member of the Folk Dance Group Yii Má}
    {Performed in the dance festival "Kupalnocka" in Poland.}
\end{entrylist}

\section{Interests}
    Dance, cuisine and spirits, makeup art, hair styling, social events, running, travel

\end{document}
